\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}). Therefore, with no lack of generality, the MR can be reduced to
\begin{displaymath}
    \text{MR} = \frc{\mu_{i}}{\mu_{j}},
\end{displaymath}
 i.e., the viscosity ratio. Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity. \red{(PARAGRAPH NEEDS TO BE IMPROVED)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Model Validation}\label{section:validation:results}

Numerical simulations performed for this work were conducted with the next generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,porosity_documentation,fluidity_manual}

%,jackson_2015,pavlidis2016

The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. \citet{salinas_2016}

@@

%%%%%%%%%%%% 
\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}

@@

\clearpage 
\listoffigures
\clearpage

\input{article_figure1}
%\input{article_figure2}

>>>>

From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}). Therefore, with no lack of generality, the MR can be reduced to a viscosity ratio,
\begin{displaymath}
    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
\end{displaymath}
 that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}. Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity. \red{(PARAGRAPH NEEDS TO BE IMPROVED)}

@@

%%%%%%%%%%%% 
\subsection{Model Set-up}\label{section:results:setup}

Numerical simulations performed in this section were conducted with the next-generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}. This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.

%%%%%%%%%%%% 
\subsection{Model Validation}\label{section:results:validation}

This The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media

The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.

@@

%%%%%%%%%%%%  
\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results:heleshaw}

@@

\listoftables
\clearpage
\input{article_table}
\clearpage  
\listoffigures
\clearpage
\input{article_figure1}
%\input{article_figure2}
